% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\href{}{\LARGE Kristian R. Kyvik}} & \href{mailto:kristianruizkyvik@gmail.com}{kristianruizkyvik@gmail.com}\\
    {\footnotesize {+34 932120948 - Cami de Vallvidrera al Tibidabo 43, 08035 Barcelona}} & \href{http://www.linkedin.com/in/kristianruizkyvik}{linkedin.com/in/kristianruizkyvik} \\
    \end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
    \begin{itemize}
        \item
            \ressubheading{\href{http://www.ntnu.edu/}{Norwegian University of Sciences and Technology}}{Trondheim, Norway}{\href{http://www.ntnu.edu/studies/mtiot}{Msc. Industrial Economics and Technology Management}; \href{}{GPA:4.06}}{Aug. 2012 -- Present}
                { \footnotesize
                \begin{itemize}
                    \resitem{Specialized in Computer Science and Communications Technology}
                    \resitem{\textbf{\href{}{ Voluntary Activities:}}}
                        \begin{itemize}
                            \resitem{ Member \& Buddy Program Coordinator at {\href{http://www.trondheim.esn.no/}{ESN (Erasmus Student Network)}}}
                            \resitem{ Member \& Main Organiser at {\href{http://www.best.eu.org/index.jsp}{BEST (Board of European Student of Technology)}}}
                            \resitem{ Workshop Contact and Performing Arts Functionary at {\href{http://www.isfit.org/tabs/about-isfit}{ISFiT (International Student Festival in Trondheim)}}}
                        \end{itemize}
                \end{itemize}
                }
        \item
        \ressubheading{\href{http://www.kcl.ac.uk/index.aspx}{King's College London}}{London, United Kingdom}{\href{}{Exchange Year (during third year)}; \href{}}{Aug. 2014 -- Jun. 2015}
            { \footnotesize
            \begin{itemize}
                \resitem{Key Courses: Artificial Intelligence, Multi-Agent Systems, Optimization Methods, Programming Applications}
            \end{itemize}
            }
        \item
        \ressubheading{\href{http://www.ntnu.edu/}{Ironhack}}{Barcelona, Spain}{\href{https://www.ironhack.com/en}{Intensive 8 week programming apprenticeship}; \href{}}{Jun. 2012 -- Aug. 2014}
            { \footnotesize
            \begin{itemize}
                \resitem{Focused on TDD, pair-programming, self-teaching/troubleshooting}
                \resitem{Learned Front-end \& Back-end development, HTML5, CSS3, JavaScript, Git, Ruby, Rails, MVC, agile methods}
            \end{itemize}
            }
    \end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
    \begin{itemize}
        \item
            \ressubheading{\href{http://www.toadlondon.com/}{TOAD London}}{London, United Kingdom}{Software Developer}{Nov. 2014 -- Aug. 2015}
                { \footnotesize
                \begin{itemize}
                    \resitem{Created responsive front-end implementations for websites and mobile apps using Bootstrap and AngularJS}
                    \resitem{Worked on back-end implementation of web-apps (NodeJS) as well as with a variety of CMS platforms}
                    \resitem{Created email marketing campaigns and used web analytic tracking systems}
                \end{itemize}
                }
        \item
            \ressubheading{\href{http://www.ntnu.edu/studies/mtiot}{Norwegian University of Sciences and Technology}}{Trondheim, Norway}
                {Learning Assistant/ Facilitator at Experts in Team (EiT)}{Jan. 2014 -- Jun. 2014}
                { \footnotesize
                \begin{itemize}
                    \resitem{EiT is a course in which students apply their academic competence in interdisciplinary projects}
                    \resitem{Observed and provided feedback on group interactions and planned activities to stimulate team dynamics}
                \end{itemize}
                }

            \ressubsubheading{Teaching Assistant in Dicrete Mathematics}{Aug. 2013 -- Feb. 2013}
                { \footnotesize
                \begin{itemize}
                    \resitem{Overlooked two weekly 2-hour tutorials in the subject TMA4140 Discrete Mathematics}
                \end{itemize}
                }

        \item
            \ressubheading{\href{http://www.moereguide.com/}{M{\o}re \& Trondelag Guideservice AS}}{Trondheim, Norway}{Tourist Guide}{Jun. 2013 -- Aug. 2013}
                { \footnotesize
                \begin{itemize}
                    \resitem{Worked as a tourist guide for both Spanish and British groups (30-50 at a time)}
                \end{itemize}
                }

    \end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
    \begin{description}
        \item[Technologies:] { \footnotesize Ruby, Python, Java, Javascript, MySQL, HTML, CSS, Rails, Angular, Bootstrap, Git, Regex, JSON}

        \item[Languages:] { \footnotesize
            Spanish (Fluent), English (Fluent), Norwegian (Advanced), Catalan (Fluent), French (Intermidiate)
        }

    \end{description} % End Skills list

\resheading{\href{http://www.derekhildreth.com/portfolio.php}{Projects}}

\begin{description}
\item[\href{https://www.no.capgemini-consulting.com/careers/management-consulting-workshop}{Attended Capgemini Management Consulting Workshop:}] { \footnotesize This four-day event held in Paris, provides a unique insight into what it means to work as a management consultant at Capgemini Consulting}

\item[\href{https://vimeo.com/107409144}{HackShow Finalist:}] { \footnotesize Made it to the top 5 projects of the IronHack cohort and presented during the final ceremony}

\item[Prize at Manchester MLH Hack:] { \footnotesize Created a mobile app that provided directions without internet connection}

\item[\href{http://elworldtrip.com/}{elWorldtrip:}] { \footnotesize Project that involved traveling around the world with my family for an entire year. The six of us crossed more than 30 countries and 5 continents in our old Toyota Land Cruiser. It was a trip to explore the world, learn about foreign cultures and, last but not least, to spread consciousness about Diabetis.}

\end{description}

\end{document}


%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".
% Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%


%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
    \begin{center}
        \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
            Toby Rummans & Eric Karl & Gordon Smith \\
            Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\
            \vspace{10pt}
            Memolinkcorp & BYU-Idaho & BYU-Idaho \\
            [removed] & 525 South Center St. & 525 South Center St.  \\
            Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
            [removed] & (208) 496-3097 & (208) 496-2816 \\
        \end{tabular*}
    \end{center}

% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED   OR OLD


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge.
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas,
reporting information, editing, interviewing, and facilitating group discussion.

- Research and Planning: The ability to search for specific knowledge and formulate a
program for a definite course of action. Skills like forecasting, predicting, identifying
issues, finding alternatives, gathering information, solving problems, setting goals,
extracting information, and developing strategies.

- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to
people, and help people. Skills like providing support for others, listening, delegating
with respect, representing others, asserting, developing rapport, and perceiving
feelings.

- Management, Organization, Leadership: The ability to supervise others and guide
individuals and groups towards the completion of tasks. Skills like managing groups,
selling ideas, making decisions, managing conflict, coordinating tasks, teaching,
enlisting help.

Source:
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources:
http://www.tvmier.com/Resume_Education.html

